# (PART) Analytical methods {-}

# Electrochemical methods

To load electrochemical data (i.e. cyclic voltammograms or bulk electrolysis) the `echem_read()` function can be used. It will try to determine the type of experiment and read it accordingly.^[If you have problems reading certain files, then please file a [Github issue](https://github.com/SPOMAN/osctools/issues) and describe the problem or a pull request with a suggested solution. Remember to add a link to the file causing problems.]

The package contains a few example files that we will use here. To use your own files, just supply the filename.

## Cyclic voltammetry
CV data can be loaded from a txt-file.
```{r}
library(osctools)

# This chould just as well be the path to your file as a string, i.e. 
# file <- "data/cv_example.txt"
file <- system.file("extdata/cv/cv_example.txt", package = "osctools")

cv1 <- echem_read(file)
cv1
```

In case that the file is just a pure CV file without any leading metadata, you will need to specify the type of experiment.

```{r}
file2 <- system.file("extdata/cv/cv_example4.txt", package = "osctools")
cv2 <- echem_read(file2, type = "CV")
```

The CV objects can be plotted directly for quick assesment. However, they probably need tweaking to your specific need before they are ready for publication.

```{r}
plot(cv1)
```

## Electrolysis
The same principles applies to loading and plotting a bulk electrolysis.

```{r}
elec1 <- echem_read(system.file("extdata/electrolysis/electrolysis_example.txt", package = "osctools"))
plot(elec1)
```

## Loading several files
It is very common to have a folder full of data-files that you want to load into one table. An easy way to do that is by making a list of the filenames and then using `purrr::map()` to iterate over the file names.

For this example we have a folder containing 4 files.

```{r}
list.files(path = "data/cv")
```

We can make a list of the file names and apply `echem_read()` to all of them.

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

path <- "data/cv/"
data <- tibble(files = list.files(path = path, pattern = "*.txt"))

# Load all data from the files into the tibble
data <- data %>% 
  mutate(d = map(paste0(path, files), echem_read)) %>% 
  unnest()
```

We can then use `ggplot2` to plot them all simultaneously.

```{r}
data %>% 
  ggplot(aes(potential, current, color = files)) + 
  geom_path()
```

